### 2011-12-22 trunk/GUIErrorDetector/paper/related.tex
tweak

Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
Harrold:2000:TR:336512.336532}.
 Many GUI analysis and testing techniques have been proposed in the past decade; some have been
implemented as tools and adopted by practitioners. Existing techniques automate
some aspect(s) of GUI testing including model creation
(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
For example,
Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
concurrently running applications. The behavior of the system under test
needs to be specified manually as a labeled transition system. 
Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
is a GUI testing framework for Java and Microsoft Windows applications. 
Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
programs. They proposed a model-based approach for testing GUI-based applications.
Their technique can generate test cases automatically using a structural event
generation graph.

%Their approach targets Java desktop applications, which
%are quite different from the Android mobile environment (XXXX).

However, testing is often insufficient to ensure the correctness of a GUI program, for
a number of reasons. First of all, the space of possible interactions
with a GUI is enormous, in that each sequence of GUI
events can result in a different state, and each GUI event
may need to be evaluated in all of these states~\cite{YuanMemonICSE2007}.
The large number of possible states result in a large number of
test inputs requiring substantile human effort. The second
problem is to determine the coverage of a set of test
cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
using the amount and type of underlying code exercised.
These measures do not work well for GUI testing, because
what matters is not only how much of the code is tested,
but in how many different possible states of the software
each piece of code is tested. This makes it hard to determine
the effectiveness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
In constrast, as advocated in this paper, the primary advantage of
using a static analysis is that it can potentially explore
all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
Compared with software testing, a static analysis tool may
report false positives due to its conservative nature. Netherless,
as we demonstrated in our experiments, using a few simple heuristics
can dramatically reduce the number of false positives  to
an acceptable level.

@@

An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
By exhaustively exploring the thread scheduling space, a model checker can
report counter examples for the potential bugs with a counter example. For example,
CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
a model checker to construct the witness for data races reported by the lockset algorithm.
%(XXXX problem for applying to GUI).
Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
 without compromising the detection capability. To our best knowledge,
we are not aware of any software model checking approach can scale to the subjects
as large as those used in our experiments. Compared with model checking, the static analysis
algorithm presented in this paper chooses call graph as the
abstraction level with a set of heuristics, and is much lightweighted. It is highly tailored to find the invalid thread
access errors instead of being a general property checking tool. For this reason,
our technique achieves good scalability and reasonable precision.

>>>>

Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
Harrold:2000:TR:336512.336532}.
 Many GUI analysis and testing techniques have been proposed in the past decade; some have been
implemented as tools and adopted by practitioners. Existing techniques automate
some aspect(s) of GUI testing including model creation
(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
For example,
Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
concurrently running applications. The behavior of the system under test
needs to be specified manually as a labeled transition system. 
Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
is a GUI testing framework for Java and Microsoft Windows applications. 
Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
programs. They proposed a model-based approach for testing GUI-based applications.
Their technique can generate test cases automatically using a structural event
generation graph. 
%Their approach targets Java desktop applications, which
%are quite different from the Android mobile environment (XXXX).
However, testing is often insufficient to ensure the correctness of a GUI program, for
a number of reasons. First of all, the space of possible interactions
with a GUI is enormous, in that each sequence of GUI
events can result in a different state, and each GUI event
may need to be evaluated in all of these states~\cite{YuanMemonICSE2007}.
The large number of possible states result in a large number of
test inputs requiring substantile human effort. The second
problem is to determine the coverage of a set of test
cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
using the amount and type of underlying code exercised.
These measures do not work well for GUI testing, because
what matters is not only how much of the code is tested,
but in how many different possible states of the software
each piece of code is tested. This makes it hard to determine
the effectiveness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
In contrast, as advocated in this paper, the primary advantage of
using a static analysis is that it can potentially explore
all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
Compared with software testing, a static analysis tool may
report false positives due to its conservative nature. Netherless,
as we demonstrated in our experiments, using a few simple heuristics
can dramatically reduce the number of false positives  to
an acceptable level.

@@

An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
By exhaustively exploring the thread scheduling space, a model checker can
report counter examples for the potential bugs with a counter example. For example,
CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
a model checker to construct the witness for data races reported by the lockset algorithm.
%(XXXX problem for applying to GUI).
Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
 without compromising the detection capability. To our best knowledge,
we are not aware of any software model checking approach can scale to the subjects
as large as those used in our experiments. Compared with model checking, the static analysis
algorithm presented in this paper chooses call graph as the
abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
access errors instead of being a general property checking tool. For this reason,
our technique achieves good scalability with reasonable precision.
